Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
L1 regularization is written \ell_1

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{center}
\texttt{clf = LogisticRegression(penalty="l1").fit(X\_train, y\_train)}
\end{center}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

@@

% By composing, say, a \texttt{CountVectorizer} object
% (which extracts term frequency features from text documents
% according to a bag-words model),
% a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
% one obtains a pipeline object with various hyperparameters:
% whether to do stopword filtering,
% linear vs.\ logarithmic \textsf{tf}, number of features to keep,
% SVM regularization ($L_1$ or $L_2$ norm, strength $C$) a.o.
% Such a composite \texttt{Pipeline} object
% exposes all of these parameters using a special syntax;
% each estimators must be given a name,
% and if the SVM's name is, e.g., \texttt{linearsvm},
% then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
% The pipeline's \texttt{set\_params} splits the parameter names
% on double underscores, uses the first part of the result
% to look up the estimator,
% and passes the second part to the estimator's own \texttt{set\_params}
% as a keyword argument; due to Python's dynamic parameter passing,
% the result is the same as if the user had called \texttt{set\_params}
% on the SVM themselves.
% (The double underscore syntax is not special to pipelines;
% it is also employed in ensemble estimators such as random forests
% % Is the following clear? Suggestions to replace "direct attributes" with"?
% It is chosen as a convention to avoid ambiguity, as direct
% attributes and methods of scikit-learn objects never contain
% double underscores.)

>>>>

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
% XXX: Gael: I think that we should break the following lines in 2: the
% 'return self' hidden in the call to fit can be confusing to the casual
% reader
\begin{center}
\texttt{clf = LogisticRegression(penalty="l1").fit(X\_train, y\_train)}
\end{center}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence
enabling $\ell_1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the training arrays \texttt{X\_train} and
\texttt{y\_train}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LogisticRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

@@

% By composing, say, a \texttt{CountVectorizer} object
% (which extracts term frequency features from text documents
% according to a bag-words model),
% a \textsf{tf--idf} transformer, a $\chi^2$ feature selector and a linear SVM,
% one obtains a pipeline object with various hyperparameters:
% whether to do stopword filtering,
% linear vs.\ logarithmic \textsf{tf}, number of features to keep,
% SVM regularization ($\ell_1$ or $\ell_2$ norm, strength $C$) a.o.
% Such a composite \texttt{Pipeline} object
% exposes all of these parameters using a special syntax;
% each estimators must be given a name,
% and if the SVM's name is, e.g., \texttt{linearsvm},
% then its $C$ parameter is exposed as \texttt{linearsvm\_\_C}.
% The pipeline's \texttt{set\_params} splits the parameter names
% on double underscores, uses the first part of the result
% to look up the estimator,
% and passes the second part to the estimator's own \texttt{set\_params}
% as a keyword argument; due to Python's dynamic parameter passing,
% the result is the same as if the user had called \texttt{set\_params}
% on the SVM themselves.
% (The double underscore syntax is not special to pipelines;
% it is also employed in ensemble estimators such as random forests
% % Is the following clear? Suggestions to replace "direct attributes" with"?
% It is chosen as a convention to avoid ambiguity, as direct
% attributes and methods of scikit-learn objects never contain
% double underscores.)
